Magic Vs Evolution

### 2024-04-02 paper/paper.qmd
made the model for darwins paper

library(tidyverse)
library(gutenbergr)
```

@@

@@

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

>>>>

library(tidyverse)
library(gutenbergr)
library(pdftools)
library(arrow)
library(dplyr)
library(stringr)
library(rstanarm)
library(marginaleffects)
```

@@

```{r}
harry <- pdf_text("../other/literature/HarryAzkaban.pdf")
class(harry)
harry <- tibble(
  raw_text = harry,
  page_number = c(1:454)
)

harry <- 
  separate_rows(harry, raw_text, sep = "\\n", convert = FALSE)

write_csv(harry, "../data/raw_data/harry.csv")

```{r}
darwin <- read_csv(
  "../data/raw_data/darwin.csv",
  col_types = cols(
    gutenberg_id = col_integer(),
    text = col_character()
  )
)

darwin_reduced <- darwin |>
  filter(!is.na(text)) |> 
  mutate(natural_count = str_count(text, regex('natural', ignore_case = T)), 
         magic_count = str_count(text, regex('magic|miracle', ignore_case = T)), 
         word_count = str_count(text, "\\w+"))

write_csv(darwin_reduced, "../data/analysis_data/darwin_reduced.csv")
arrow::write_parquet(darwin_reduced, "../data/analysis_data/darwin_reduced.parquet")
```

@@

## Natural and the 2 texts

Define $y_i$ is the number of times "natural" appeared in the text and the explanatory variable is the number of words in the line.

\begin{align} 
y_i|\lambda_i &\sim \mbox{Poisson}(\lambda_i) \\
\mbox{log}(\lambda_i) &= \beta_0 + \beta_1 \times \mbox{Number } \mbox{of } \mbox{Words}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
```{r}
darwin_nature <-
  stan_glm(
    natural_count ~ word_count,
    data = darwin_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  darwin_nature,
  file = "../models/darwin_nature.rds"
)
```

```{r}
plot_predictions(darwin_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
Negative relation it seems

## "Magic" and the 2 texts
Define $y_i$ is the number of times "magic" or "miracle" appeared in the text and the explanatory variable is the number of words in the line.

\begin{align} 
y_i|\lambda_i &\sim \mbox{Poisson}(\lambda_i) \\
\mbox{log}(\lambda_i) &= \beta_0 + \beta_1 \times \mbox{Number } \mbox{of } \mbox{Words}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\end{align}
